---
title: "Homework 1"
author: Maya Bunyan
output: github_document
---

This is my solution to Homework 1! 

```{r load_packages}
library(tidyverse)
library(ggplot2)
```

## Problem 1

Create a data frame comprised on the listed elements.

```{r create_df}
problem1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_zero = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    fac_vec = factor(c("low", "low", "low", "med", "med", "med", "med", "high", "high", "high"))
  )
```

Take mean of each variable in the data frame problem1_df.

```{r get_means}
mean(pull(problem1_df, samp))
mean(pull(problem1_df, samp_gt_zero))
mean(pull(problem1_df, char_vec))
mean(pull(problem1_df, fac_vec))
```

I am able to take the mean of numbers and the logical vector, but cannot take the mean for the character and factor vectors.



Convert the variables in the data frame problem1_df to numeric.

```{r make_numeric, results='hide', warning=FALSE}
as.numeric(pull(problem1_df, samp))
as.numeric(pull(problem1_df, samp_gt_zero))
as.numeric(pull(problem1_df, char_vec))
as.numeric(pull(problem1_df, fac_vec))
```

The random sample and logical vector are able to be converted into numeric format, but the character and factor vector are not able to be converted into the numeric format. This is because the random sample is already numeric and logical vectors are able to be changed into numeric values. R is not able to do the same for character and factor vectors, so they are changed to NA. This explains why we were able to take the mean for the random sample and logical vector, but not the character and factor vectors.



Covert logical vector to specified vector type and multiply by random sample result.

```{r convert_multiply}
as.numeric(pull(problem1_df, samp_gt_zero)) * pull(problem1_df, samp)
as.factor(pull(problem1_df, samp_gt_zero)) * pull(problem1_df, samp)
as.numeric(as.factor(pull(problem1_df, samp_gt_zero))) * pull(problem1_df, samp)
```


## Problem 2

Load penguins dataset and write short description of the data using inline code.

```{r load_data}
data("penguins", package = "palmerpenguins")
```

The penguins dataset has `r ncol(penguins)` variables and `r nrow(penguins)` data points. It focuses on the penguin species `r levels(pull(penguins, species))`, who live on `r levels(pull(penguins, island))` islands. Other variables in the dataset include, `r names(penguins)[3:8] `. The penguins in the sample have an average bill length of `r mean(pull(penguins, bill_length_mm), na.rm = T)` mm, an average bill depth of `r mean(pull(penguins, bill_depth_mm), na.rm = T)` mm, an average flipper length of `r mean(pull(penguins, flipper_length_mm), na.rm = T)` mm, and an average body mass of `r mean(pull(penguins, body_mass_g), na.rm = T)` g. 



Create scatterplot of flipper length versus bill length with different colored points to denote different species, and export.

```{r flipper_bill_scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("flipper_bill_scatterplot.pdf")
```

