---
title: "Homework 1"
author: Maya Bunyan
output: github_document
---

This is my solution to Homework 1! 

```{r load_packages}
library(tidyverse)
```

## Problem 1

Create a data frame comprised on the listed elements.

```{r create_df}
problem1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_zero = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    fac_vec = factor(c("low", "low", "low", "med", "med", "med", "med", "high", "high", "high"))
  )
```

Take the mean of each variable in the data frame problem1_df.

```{r get_means}
mean(pull(problem1_df, samp))
mean(pull(problem1_df, samp_gt_zero))
mean(pull(problem1_df, char_vec))
mean(pull(problem1_df, fac_vec))
```

I am able to take the mean of numbers and the logical vector, but cannot take the mean for the character and factor vectors.



Convert the variables in the data frame problem1_df to numeric.

```{r make_numeric, results='hide', warning=FALSE}
as.numeric(pull(problem1_df, samp))
as.numeric(pull(problem1_df, samp_gt_zero))
as.numeric(pull(problem1_df, char_vec))
as.numeric(pull(problem1_df, fac_vec))
```

The logical and factor vectors are able to be converted into numeric format, but the character vector is not. This is because logical vectors are stored in the back-end as numeric values. This explains why we were able to take the mean for the logical vector. We can also force R to convert a factor vector into numeric, which is why it is converted to numeric here. However, it does not usually do that, so that is why we were not able to get a mean for it previously. We cannot force R to convert character vectors to numeric, so the values are changed to NA and, thus, a mean was not able to be calculated. 


Covert the logical vector to specified vector type and multiply by random sample result.

```{r convert_multiply}
as.numeric(pull(problem1_df, samp_gt_zero)) * pull(problem1_df, samp)
as.factor(pull(problem1_df, samp_gt_zero)) * pull(problem1_df, samp)
as.numeric(as.factor(pull(problem1_df, samp_gt_zero))) * pull(problem1_df, samp)
```


## Problem 2

Load penguins dataset and write short description of the data using inline code.

```{r load_data}
data("penguins", package = "palmerpenguins")
```

The penguins dataset has `r ncol(penguins)` variables and `r nrow(penguins)` data points. It focuses on `r nlevels(pull(penguins, species))` penguin species, `r levels(pull(penguins, species))`, on `r nlevels(pull(penguins, island))` islands, `r levels(pull(penguins, island))`. Other variables in the dataset include, `r names(penguins)[3:8] `. The penguins in the sample have an average bill length of `r mean(pull(penguins, bill_length_mm), na.rm = T)` mm, an average bill depth of `r mean(pull(penguins, bill_depth_mm), na.rm = T)` mm, an average flipper length of `r mean(pull(penguins, flipper_length_mm), na.rm = T)` mm, and an average body mass of `r mean(pull(penguins, body_mass_g), na.rm = T)` g. 



Create a scatterplot of flipper length versus bill length with different colored points to denote different species, and export.

```{r flipper_bill_scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("flipper_bill_scatterplot.pdf")
```

